UQWorld: an Applied UQ Community

### 2019-05-09 latex/uqworld-presentation.tex
Minor edit

Some are a bit hard to read,
\begin{itemize}
  \item From: $\blacksquare@\blacksquare$.edu.cn, Subject: Matlab code by Dr. Moustapha w.r.t. the fascinating Quantile-based RBDO
  \begin{quotation}
    Good dinner Dr. Moustapha \\
    Your catchy Quantile-based RBDO bring up new ideas for our RBDO world.
    If Dr. Moustapha is going to need allies or assistants for your idea to gain momentum, sincere hope for good cooperation (fans) between us (of yours) \texttt{\textasciitilde.\textasciitilde}!
    Actually, me is a current Master student w.r.t. Reliabil \& Syst Engn.
    If I make the decision to embark on a PhD, your QB-RBDO is really fascinating for me.(Wow! Such a productve and effective methodology for practical applications.That's terrific!)
  \end{quotation}
\end{itemize}

@@

\begin{tabularx}{\textwidth}{XXXX}
  \hline
                                    & Inception    & Establishment  & Maturity \\
  \hline
  \footnotesize{Majority of members}
  & Core members, UQLab users
  & UQLab users, UQ practitioners
  & UQ practitioners and researchers  \\

>>>>

Praise? Collaboration inquiry?
\begin{itemize}
  \item From: $\blacksquare@\blacksquare$.edu.cn, Subject: Matlab code by Dr. Moustapha w.r.t. the fascinating Quantile-based RBDO
  \begin{quotation}
    Good dinner Dr. Moustapha \\
    Your catchy Quantile-based RBDO bring up new ideas for our RBDO world.
    If Dr. Moustapha is going to need allies or assistants for your idea to gain momentum, sincere hope for good cooperation (fans) between us (of yours) \texttt{\textasciitilde.\textasciitilde}!
    Actually, me is a current Master student w.r.t. Reliabil \& Syst Engn.
    If I make the decision to embark on a PhD, your QB-RBDO is really fascinating for me.(Wow! Such a productve and effective methodology for practical applications.That's terrific!)
  \end{quotation}
\end{itemize}

@@

\begin{tabularx}{\textwidth}{XXXX}
  \hline
                                    & Inception    & Establishment  & Maturity \\
  \hline
  \footnotesize{Majority of members}
  & Core members (+invitees), UQLab users
  & UQLab users, UQ practitioners
  & UQ practitioners and researchers  \\
